\documentclass[a4paper,12pt]{article}
%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
%tabularx environment
\usepackage{tabularx}
%for lists within experience section
\usepackage{enumitem}
% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 
%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}
%for social icons
\usepackage{fontawesome5}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,noitemsep]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}


\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}}\\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}
    \end{tabular*}
}

\newcommand{\resumeExperience}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}}\\
        \textit{\footnotesize{#2}} & {}
    \end{tabular*}\\ [1mm]
    \footnotesize{#4}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
}
\newcommand{\emptyLine}{\\[-3mm]}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Vinay Saini} \\[7.5pt]
{Full-Stack Software Development Engineer} \\[7.5pt]
\href{https://github.com/vnyseny}{\raisebox{-0.05\height}\faGithub\ vnyseny} \ $|$ \ 
\href{https://linkedin.com/in/vnyseny}{\raisebox{-0.05\height}\faLinkedin\ in/vnsyseny} \ $|$ \ 
%\href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
\href{mailto:vnyseny@gamil.com}{\raisebox{-0.05\height}\faEnvelope \ vnyseny@gamil.com} \ $|$ \ 
\href{tel:+917015834371}{\raisebox{-0.05\height}\faMobile \ +91-7015834371} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Dedicated Full-Stack Software Development Engineer with a strong background in developing innovative solutions for the banking and financial sector. Skilled in designing, implementing, and maintaining robust software applications to meet the complex needs of financial institutions. Experienced in the entire software development life-cycle, from concept to deployment, with a focus on delivering high-quality, scalable solutions.

%Education
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kurukshetra University, Kurukshetra}{Percentage: 78}
      {Bachelor of Technology (Computer Science and Engineering)}{2017 - 2021}
    \resumeSubheading
      {Govt. Polytechnic Sonipat}{Percentage: 60}
      {Polytechnic Diploma (Electrical Engineering)}{2012 - 2015}
    \resumeSubheading
      {Board of School Education Haryana, Bhivani}{Percentage: 84}
      {Class 10th}{2012}
  \resumeSubHeadingListEnd
  
%Experience
\section{Work Experience}

\resumeSubHeadingListStart
\resumeExperience {Surya Software Systems Private Limited, Bengaluru}
 {Software Development Engineer} {Jan 2022 - Present}
{
As a Software Development Engineer at Surya Software Systems Private Limited, I play a key role in software development using \textbf{ASP.NET} and \textbf{.NET Core}. My responsibilities include:
}\emptyLine
\resumeItemListStart
    \item Collecting requirements from clients
    \item Preparing technical specifications
    \item Developing dynamic \textbf{web forms} for data input and interaction, utilizing \textbf{ASP.NET} technologies
    \item \textbf{Backend} and \textbf{frontend} development, focusing on creating robust and scalable solutions
    \item Optimizing code, fixing bugs, and ensuring smooth deployment processes
    \item Developing \textbf{analytics reports} for data analysis and visualization
    \item Providing leadership in my team, guiding and mentoring junior developers
    \item Contributing to project migration and \textbf{ETL} processes, ensuring seamless transitions and efficient data processing
    \resumeItemListEnd
\resumeSubHeadingListEnd

%Projects
\section{Projects}

\resumeSubHeadingListStart
\resumeExperience {Bloggie} 
{Bloggie is a blog application, offering a platform for users to create, edit, and publish blog posts.}
{\href{https://vnyseny.bsite.net/}{Link to Demo}}
{}
      \resumeItemListStart
        \item {The application was developed using the \textbf{ASP.NET Core MVC} framework.}
        \item {\textbf{Designed} and implemented the \textbf{database schema} for the blog application.}
        \item {Developed the \textbf{front-end} and \textbf{back-end} functionality for creating and managing blog posts.}
        \item {The application allows registered users to manage their posts and comments with \textbf{Authentication}.}
        \item {Utilized \textbf{Entity Framework }Core for data access and \textbf{SQL Server} for database management.}
        \item {Employed \textbf{Razor} syntax for dynamic content rendering and \textbf{Bootstrap} for front-end styling.}
        \item {Integrated user authentication and authorization features using \textbf{ASP.NET Core Identity} for secure access.}\\
    \resumeItemListEnd
\resumeExperience {Attendance by Face Detection} 
{Transforming attendance management through advanced face detection technology.}
{}
{}
      \resumeItemListStart
        \item {Developed a sophisticated face recognition system in \textbf{Python} using the \textbf{OpenCV}, \textbf{NumPy}, and \\ \textbf{face\_recognition} libraries.}
        \item {The system is capable of detecting \textbf{human faces} in \textbf{images} and \textbf{video streams} using \textbf{OpenCV}, storing and comparing facial encodings using \textbf{NumPy arrays} for efficient processing.}
        \item {Leveraged the face\_recognition library to access a \textbf{pre-trained} model for recognizing human faces with high accuracy.}
        \item {Employed NumPy for storing and comparing facial encodings, ensuring fast and reliable face recognition.}
        \item {Implemented a user-friendly interface for displaying detected faces }\\
    \resumeItemListEnd
\resumeExperience {Tic Tac Toe (Game)} 
{Play Tic Tac Toe: A Classic Game of Strategy and Fun!}
{\href{https://vnyseny.github.io/tic-tac-toe/}{Link to Demo}}
{}
      \resumeItemListStart
    \item Tic Tac Toe is a timeless game where players strategically place their markers (X or O) in a 3x3 grid.
    \item The goal is to create a row, column, or diagonal of their markers to win the game.
    \item The project helped solidify JavaScript programming skills.
    \item It provided hands-on experience in developing a complete web application using JavaScript, HTML, and CSS.
    \item The project taught valuable lessons in user interface design.
    \item It offered insights into game development.
    \item It provided practical experience in project management.\\
    \resumeItemListEnd
\resumeExperience {Snake Game} 
{Snake Game: A Classic Game of Fun!}
{}
{}
      \resumeItemListStart
    \item Used JAVA for development.
    \item The Swing library was employed to create the window-based application.
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------Technical skills-----------------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, Javascript, Java, Python, SQL, XML} \\
     \textbf{Developer Tools}{: Visual Studio, VS Code, Git, Github } \\
     \textbf{Frameworks/Libraries}{: ASP.NET, .NET(Dotnet), ReactJs, MVC, MVVM, Blazor, JQuery, Entity Framework, LINQ } \\
     \textbf{Coursework}{: Data Structures \& Algorithms, SDLC, Object Oriented Programming, Database Management System, Software Engineering.} \\
     % \textbf{Areas of Interest}{: } \\
     \textbf{Other Skills}{: Azure DevOps, Linux, API, WCF, WPF} \\
     \textbf{Soft Skills}{: Self-learning, Presentation, Adaptability, Communication, Teamwork, Problem-solving, Leadership, Time Management, Critical Thinking, Emotional Intelligence} \\
    }}
 \end{itemize}

\vfill
% \center{\footnotesize Last updated: \today}

\end{document}
