\documentclass[a4paper,12pt]{article}
%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
%tabularx environment
\usepackage{tabularx}
%for lists within experience section
\usepackage{enumitem}
% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 
%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}
%for social icons
\usepackage{fontawesome5}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,noitemsep]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}


\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}}\\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}
    \end{tabular*}
}

\newcommand{\resumeExperience}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}}\\
        \textit{\footnotesize{#2}} & {}
    \end{tabular*}\\ [1mm]
    \footnotesize{#4}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
}
\newcommand{\emptyLine}{\\[-3mm]}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Vinay Saini} \\[7.5pt]
{Full-Stack Software Development Engineer} \\[7.5pt]
\href{https://github.com/vnyseny}{\raisebox{-0.05\height}\faGithub\ vnyseny} \ $|$ \ 
\href{https://linkedin.com/in/vnyseny}{\raisebox{-0.05\height}\faLinkedin\ in/vnsyseny} \ $|$ \ 
%\href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
\href{mailto:vnyseny@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ vnyseny@gmail.com} \ $|$ \ 
\href{tel:+917015834371}{\raisebox{-0.05\height}\faMobile \ +91-7015834371} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Dedicated Full-Stack Software Development Engineer with a strong background in developing innovative solutions for the banking and financial sector. Skilled in designing, implementing, and maintaining robust software applications to meet the complex needs of financial institutions. Experienced in the entire software development life-cycle, from concept to deployment, with a focus on delivering high-quality, scalable solutions.

%Education
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kurukshetra University, Kurukshetra}{Percentage: 78}
      {Bachelor of Technology (Computer Science and Engineering)}{2017 - 2021}
    \resumeSubheading
      {Govt. Polytechnic Sonipat}{Percentage: 60}
      {Polytechnic Diploma (Electrical Engineering)}{2012 - 2015}
    \resumeSubheading
      {Board of School Education Haryana, Bhivani}{Percentage: 84}
      {Class 10th}{2012}
  \resumeSubHeadingListEnd

%-----------Technical skills-----------------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, Javascript, Typescript, Java, Python, SQL, HTML, XML} \\
     \textbf{Developer Tools}{: Visual Studio, VS Code, Git, Github } \\
     \textbf{Frameworks/Libraries}{: ASP.NET, .NET(Dotnet), ReactJs, Angular, MVC, MVVM, Blazor, Bootstrap, JQuery, Entity Framework, LINQ, Serilog, OpenXML } \\
     \textbf{Coursework}{: Data Structures \& Algorithms, SDLC, Object Oriented Programming, Database Management System, Software Engineering.} \\
     % \textbf{Areas of Interest}{: } \\
     \textbf{Other Skills}{: Azure DevOps, IIS ,Linux, REST API, SOAP, WPF} \\
     \textbf{Soft Skills}{: Self-learning, Presentation, Adaptability, Communication, Teamwork, Problem-solving, Leadership, Time Management, Critical Thinking, Emotional Intelligence} \\
    }}
 \end{itemize}

%Experience
\section{Work Experience}

\resumeSubHeadingListStart
\resumeExperience {Policybazaar Insurance Brokers Private Limited, Gurgaon}
 {Senior Technical Associate} {Sep 2024 - Present}
 {}
\resumeItemListStart
    \item \textbf{Development \& Maintenance:} Design, develop, and maintain scalable software solutions in alignment with business requirements. Utilize technologies such as .NET, ASP.NET Core, and SQL databases.
    \item \textbf{Project Management:} Collaborate with cross-functional teams, manage project timelines, and ensure timely delivery of software features and updates.
    \item \textbf{Quality Assurance:} Ensure code quality through unit testing and peer reviews, and resolve bugs in a timely manner.
    \item \textbf{Continuous Improvement:} Contribute to optimizing software architecture, improving performance, and adopting best practices for coding and system efficiency.
    \item \textbf{Support \& Troubleshooting:} Provide technical support for the application, troubleshoot issues, and ensure high availability of the services.
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeExperience {Surya Software Systems Private Limited, Bengaluru}
 {Software Development Engineer} {Jan 2022 - Sept 2024}
{
As a Software Development Engineer at Surya Software Systems Private Limited, I play a key role in software development using \textbf{ASP.NET(C\#)} and \textbf{.NET Core(C\#)}. My responsibilities include:
}\emptyLine
\resumeItemListStart
    \item \textbf{Gathering Client Requirements:} Collaborated closely with clients to understand their needs and translate them into detailed technical specifications.
    \item \textbf{Technical Documentation:} Prepared comprehensive technical specifications to guide development processes.
    \item \textbf{Dynamic Web Forms Development:} Designed and developed dynamic web forms for efficient data input and user interaction using ASP.NET technologies.
    \item \textbf{Code Optimization and Bug Fixing:} Optimized code for performance, resolved complex bugs, and ensured seamless deployment across multiple environments.
    \item \textbf{Analytics and Reporting:} Developed sophisticated analytics reports to facilitate data analysis and visualization for informed decision-making.
    \item \textbf{Full-Stack Development:} Led both backend and frontend development efforts, ensuring the creation of robust, scalable, and responsive solutions.
    \item \textbf{Team Leadership and Mentorship:} Provided leadership within the team, mentoring junior developers and guiding them through project challenges.
    \item \textbf{Project Migration and ETL:} Managed project migrations and ETL processes, ensuring smooth transitions, data integrity, and efficient processing.
    \item \textbf{Deployment Management:} Managed the deployment of applications using IIS, ensuring reliable and secure hosting in a production environment.
    \item \textbf{Projects:} Contributed to key projects including PFS (Planning and Forecasting System), FTP (Fund Transfer Pricing), BASEL, Risk Aggregator, RControl, BALM (Bank Asset Liability Management), and IA (Income Analysis).
    \resumeItemListEnd
\resumeSubHeadingListEnd

%Projects
\section{Projects}

\resumeSubHeadingListStart
\resumeExperience {Bloggie} 
{Bloggie is a blog application, offering a platform for users to create, edit, and publish blog posts.}
{\href{https://vnyseny.bsite.net/}{Link to Demo}}
{}
      \resumeItemListStart
        \item {The application was developed using the \textbf{ASP.NET Core MVC} framework.}
        \item {\textbf{Designed} and implemented the \textbf{database schema} for the blog application.}
        \item {Developed the \textbf{front-end} and \textbf{back-end} functionality for creating and managing blog posts.}
        \item {The application allows registered users to manage their posts and comments with \textbf{Authentication}.}
        \item {Utilized \textbf{Entity Framework }Core for data access and \textbf{SQL Server} for database management.}
        \item {Employed \textbf{Razor} syntax for dynamic content rendering and \textbf{Bootstrap} for front-end styling.}
        \item {Integrated user authentication and authorization features using \textbf{ASP.NET Core Identity} for secure access.}\\
    \resumeItemListEnd
\resumeExperience {Attendance by Face Detection} 
{Transforming attendance management through advanced face detection technology.}
{}
{}
      \resumeItemListStart
        \item {Developed a sophisticated face recognition system in \textbf{Python} using the \textbf{OpenCV}, \textbf{NumPy}, and \\ \textbf{face\_recognition} libraries.}
        \item {The system is capable of detecting \textbf{human faces} in \textbf{images} and \textbf{video streams} using \textbf{OpenCV}, storing and comparing facial encodings using \textbf{NumPy arrays} for efficient processing.}
        \item {Leveraged the face\_recognition library to access a \textbf{pre-trained} model for recognizing human faces with high accuracy.}
        \item {Employed NumPy for storing and comparing facial encodings, ensuring fast and reliable face recognition.}
        \item {Implemented a user-friendly interface for displaying detected faces }\\
    \resumeItemListEnd
\resumeSubHeadingListEnd



\vfill
% \center{\footnotesize Last updated: \today}

\end{document}
